The Splashback Radius of Planck-SZ clusters

### 2019-02-20 Paper_v2/RSP_paper_new.tex
small typo edit

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal.
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}.
\textbf{We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
$s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
\citet{more2016detection} we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and
$\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
their work in order to stay conservative. We also use a normal prior with a
central value of $\log_{10}(0.2)$ for $\log_{10}(\alpha)$ as deduced from mass
estimates \citep{gao2008redshift}. To be conservative, we once again double the
scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use normal priors
with central values $\log_{10}(6.0)$ and $\log_{10}(4.0)$, respectively and
scale 0.4 as recommended by \citet{diemer2014dependence}.}

>>>>

Therefore the model is described by eight model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function to the measured two-dimensional correlation signal.
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}.
\textbf{We let the parameters $\rho_{\mathrm{s}}$, $\rho_0$ and
$s_{\mathrm{e}}$ vary freely during our fitting procedure. Similar to
\citet{more2016detection} we put flat priors on $\log_{10}(r_{\mathrm{s}})$ and
$\log_{10}(r_{\mathrm{t}})$ but double their ranges to $[0.1,5.0]$ compared to
their work in order to stay conservative. We also use a normal prior with a
central value of $\log_{10}(0.2)$ for $\log_{10}(\alpha)$ as deduced from mass
estimates \citep{gao2008redshift}. To be conservative, we once again double the
scale of the prior to be 1.2 compared to \citet{more2016detection}. For the
parameters $\log_{10}(\beta)$ and $\log_{10}(\gamma)$ we also use
normal priors with central values $\log_{10}(6.0)$ and
$\log_{10}(4.0)$, respectively. The scale of the priors is again
doubled compared to \citet{more2016detection} and set equal to 0.4.}
